An Approach for the Reduction of Boundary Effects in Time-Frequency Representations:\\ Part II

### 2020-05-27 Notes/Supplementary material/SupMat.tex
update code

\usepackage{graphicx}
\usepackage{bbm}
\usepackage{amsfonts,amssymb,amsmath,amsthm}
\usepackage{type1cm,eso-pic,color}
\usepackage{mathrsfs} 
\usepackage{mathpazo}
\usepackage[scaled=.95]{helvet}
\usepackage{courier}
\usepackage{xr}
\usepackage{xspace}
\usepackage{etoolbox}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{algorithm,algorithmic}

@@

\section{Proof of Lemma~1}
\label{ap:lm.error}
We have:
\begin{align}
\dfrac1K\bX\bX^T &= \underbrace{\dfrac1K\bZ\bZ'+\sigma^2\bI}_{\defeq S^{(0)}} + \bE^{(0)} \\
\dfrac1K\bY\bX^T &= \underbrace{\dfrac1K\bZ\bZ^T +\sigma^2\bD}_{\defeq S^{(1)}}+ \bE^{(1)} \ ,
\end{align}
where $\bE^{(a)} = \sigma\bE_1^{(a)} + \sigma^2\bE_2^{(a)}$ with:
\[
\bE_1^{(a)}[m,m'] = \dfrac1K\sum_{k=0}^{K-1} \bz[N_0+m+a+k]\bw[N_0+m'+k] + \bw[N_0+m+a+k]\bz[N_0+m'+k]\ ,
\]
and
\[
\bE_2^{(a)}[m,m'] =  \dfrac1K\sum_{k=0}^{K-1} \bw[N_0+m+a+k]\bw[N_0+m'+k] - \delta_{(m+a)m'}\ ,
\]
with $a\in\{0,1\}$.
\begin{remark}
The matrices $\bE^{(0)}$ and $\bE^{(1)}$ are said to be error matrices because:
\begin{align*}
\EE\{\bE^{(0)}\} &= \EE\{\bE_1^{(0)}\} = \EE\{\bE_2^{(0)}\} = \bzero \\
\EE\{\bE^{(1)}\} &= \EE\{\bE_1^{(1)}\} = \EE\{\bE_2^{(1)}\} = \bzero\ .
\end{align*}
\end{remark}
Thus:
\begin{align*}
\tilde\bA &= (\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv \\
\bA_0&=\bS^{(1)}{\bS^{(0)}}^\inv
\end{align*}
Then:
\begin{align}
\nonumber
\bh^{(\ell)} &= \balpha^{(\ell)} - \balpha^{(\ell)}_0 \\
\nonumber
&= \be_M^T\left(\tilde\bA^\ell-\tilde\bA_0^\ell\right) \\
&= \be_M^T\left(\left((\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\right)^\ell- \tilde\bA_0^\ell\right)\ .
\label{eq:error.vec}
\end{align}
Thus, the randomness of $\bh^{(\ell)}$ is completely originating from the random vector $\bg\in\RR^{M(M+1)}$ defined as:
\[
\bg = \vec\left(
\begin{pmatrix}
\bE^{(0)} \\
\be_M^T\bE^{(1)}
\end{pmatrix}
\right)\ .
\]
{\color{blue}
Thus, one can write $\bh^{\ell}$ as $\bh^{\ell}=f^{(\ell)}(g)$ where $f^{(\ell)}$ is a deterministic function:
\begin{align*}
f^{(\ell)} : \RR^{M(M+1)} &\to \RR^{M} \\
 \bg &\mapsto \bh^{(\ell)}\ . \\
\end{align*}
Besides, by application of the central limit theorem, the random vector $\bg$ converges in law to a Gaussian random vector:
\[
\sqrt{K}\ \bg \xrightarrow[K\to\infty]{\cD} \cN(\bzero,\bGamma_0)\ .
\]
Then, using Delta method, we have:
\begin{align*}
\sqrt{K}\ \bh^{(\ell)} \xrightarrow[K\to\infty]{\cD} \cN(\bzero,{\bF^{(\ell)}}^T\bGamma_0\bF^{(\ell)})\ ,
\end{align*}
where:
\[
\bF^{(\ell)}[m,m'] = \left.\dfrac{\partial f^{(\ell)}_m}{\partial\bg[m']}\right\vert_{\bg=\bzero}\ .
\]
}

@@

\paragraph{Expression of the bias $\bmu$.}

@@

{\color{blue}

@@

\EE\{\bh^{(\ell)}\} &\underset{K\to\infty}{=} o\left(\dfrac1{\sqrt{K}}\right)\\
\EE\{\bh^{(\ell)}\bw_{K}\} &\underset{K\to\infty}{=} o\left(\dfrac1{\sqrt{K}}\right)

@@

@@

\paragraph{Expression of the covariance $\bgamma$.}
Let us segregate the cases.

First, when $(n,n')\in I^2$, we clearly have $\bgamma[n,n']=\sigma^2\delta_{n,m}$.

Second, we focus on the case where $n=N-1+\ell\geq N$ and $n'=N-1+\lambda\geq N$. Thus:
\begin{align*}  
\bgamma[n,n'] &= \bz_K^T\EE\left\{{\balpha^{(\ell)}}^T\balpha^{(\lambda)}\right\}\bz_K + \sigma\EE\{\balpha^{(\ell)}\bw_K\balpha^{(\lambda)}\}\bz_K+ \sigma\EE\{\balpha^{(\lambda)}\bw_K\balpha^{(\ell)}\}\bz_K \\
& +\sigma^2\EE\{\balpha^{(\ell)}\bw_K\balpha^{(\lambda)}\bw_K\}-\bz[n]\bz[n']-\bz[n]\bmu[n']-\bz[n]\bmu[n'] - \bmu[n]\bmu[n'] \\
&= \bz_K^T\EE\left\{{\bh^{(\ell)}}^T\bh^{(\lambda)}\right\}\bz_K + \balpha_0^{(\ell)}\sigma\EE\{\bw_K\bh^{(\lambda)}\}\bz_K + \sigma\EE\{\bh^{(\ell)}\bw_K\}\bz(n']  \\
&+ \sigma\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\}\bz_K+ \sigma\EE\{\bh^{(\lambda)}\bw_K\}\bz[n] + \sigma\balpha_0^{(\lambda)}\EE\{\bw_K\bh^{(\ell)}\}\bz_K \\
& + \sigma\EE\{\bh^{(\lambda)}\bw_K\bh^{(\ell)}\}\bz_K+\sigma^2\balpha_0^{(\ell)}\EE\{\bw_K\bh^{(\lambda)}\bw_K\}+\sigma^2\balpha_0^{(\lambda)}\EE\{\bw_K\bh^{(\ell)}\bw_K\} \\
&+\sigma^2\left\langle\balpha^{(\ell)},\balpha^{(\ell)}\right\rangle +\sigma^2\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\bw_K\} + o(\sigma^2)
\end{align*}
From lemma~1, we have:
To be continued...

Third, we focus on the case where $n=N-1+\ell\geq N$ and $n'\in I$. The case $n\in I$ and $n'=N-1+\lambda$ is directly derived from the current one.
To be continued...
%\begin{align*}
%\bgamma[\ell,\ell] &\leq \dfrac1K\left(\sqrt{\bz_K^T\EE\{{\bu^{(\ell)}}^T\bu^{(\ell)}\}\bz_K} + \sigma\sqrt{\EE\{(\bu^{(\ell)}\bw_K)^2\}}\right)^2 \\
%&\ + \dfrac{2\sigma}{\sqrt{K}}\|\balpha_0^{(\ell)}\|\left(\sqrt{\bz_K^T\EE\{{\bu^{(\ell)}}^T\bu^{(\ell)}\}\bz_K} +\sigma\sqrt{\EE\{(\bu^{(\ell)}\bw_K)^2\}} \right)+ \sigma^2\|\balpha_0^{(\ell)}\|^2 - \bmu[\ell]^2 + o(\sigma^2) \\
%\end{align*}
%
%Then, Isserlis formula gives us:
%\begin{align*}
%\EE\{(\bu^{(\ell)}\bw_K)^2\} &= \sum_{m,m'=0}^{M-1}\EE\{\bu^{(\ell)}[m]\bw_K[m]\bu^{(\ell)}[m']\bw_K[m']\}\\
%&\underset{K\to\infty}{\sim} \sum_{m,m'=0}^{M-1}\EE\{\bu^{(\ell)}[m]\bw_K[m]\}\EE\{\bu^{(\ell)}[m']\bw_K[m']\}+\EE\{\bu^{(\ell)}[m]\bu^{(\ell)}[m']\}\EE\{\bw_K[m]\bw_K[m']\} \\
%&\hspace{30pt}+\EE\{\bu^{(\ell)}[m]\bw_K[m']\}\EE\{\bu^{(\ell)}[m']\bw_K[m]\}\\
%&\leq \Tr(\bGamma^{(\ell)}) + 2\sum_{m,m'=0}^{M-1}\sqrt{\bGamma^{(\ell)}[m,m]\bGamma^{(\ell)}[m',m']}
%\end{align*}
%So:
%\begin{align*}
%\bgamma[\ell,\ell] &\leq \dfrac1K\left(\sqrt{\bz_K^T\bGamma^{(\ell)}\bz_K} + \sigma\sqrt{\Tr(\bGamma^{(\ell)}) + 2\sum_{m,m'=0}^{M-1}\sqrt{\bGamma^{(\ell)}[m,m]\bGamma^{(\ell)}[m',m']}}\right)^2 \\
%&\ + \dfrac{2\sigma}{\sqrt{K}}\|\balpha_0^{(\ell)}\|\left(\sqrt{\bz_K^T\bGamma^{(\ell)}\bz_K} +\sigma\sqrt{\Tr(\bGamma^{(\ell)}) + 2\sum_{m,m'=0}^{M-1}\sqrt{\bGamma^{(\ell)}[m,m]\bGamma^{(\ell)}[m',m']}} \right)+ \sigma^2\|\balpha_0^{(\ell)}\|^2 + o(\sigma^2) \\
%\end{align*}
}

>>>>

\usepackage{graphicx}
\usepackage{bbm}
\usepackage{amsfonts,amssymb,amsmath,amsthm}
\usepackage{type1cm,eso-pic,color}
\usepackage{mathrsfs} 
\usepackage{mathpazo}
\usepackage[scaled=.95]{helvet}
\usepackage{courier}
\usepackage{xr}
\usepackage{xspace}
\usepackage{etoolbox}
\usepackage[shortlabels]{enumitem}
\usepackage{multirow}
\usepackage{dsfont}
\usepackage{hhline}
\usepackage{algorithm,algorithmic}
\usepackage{xr}
\externaldocument[I-]{../BoundEffRed}

@@

\section{Proof of Lemma~1}
\label{ap:lm.error}

\subsection{Notations}
We have:
\begin{align}
\dfrac1K\bX\bX^T &= \underbrace{\dfrac1K\bZ\bZ^T+\sigma^2\bI}_{\defeq S^{(0)}} + \bE^{(0)} \\
\dfrac1K\bY\bX^T &= \underbrace{\dfrac1K\bZ'\bZ^T +\sigma^2\bD}_{\defeq S^{(1)}}+ \bE^{(1)} \ ,
\end{align}
where $\bE^{(a)} = \sigma\bE_1^{(a)} + \sigma^2\bE_2^{(a)}$ with:
\[
\bE_1^{(a)}[m,m'] = \dfrac1K\sum_{k=0}^{K-1} \bz[N_0+m+a+k]\bw[N_0+m'+k] + \bw[N_0+m+a+k]\bz[N_0+m'+k]\ ,
\]
and
\[
\bE_2^{(a)}[m,m'] =  \dfrac1K\sum_{k=0}^{K-1} \bw[N_0+m+a+k]\bw[N_0+m'+k] - \delta_{(m+a)m'}\ ,
\]
with $a\in\{0,1\}$.

\begin{remark}
The matrices $\bE^{(0)}$ and $\bE^{(1)}$ are said to be error matrices because:
\begin{align*}
\EE\{\bE^{(0)}\} &= \EE\{\bE_1^{(0)}\} = \EE\{\bE_2^{(0)}\} = \bzero \\
\EE\{\bE^{(1)}\} &= \EE\{\bE_1^{(1)}\} = \EE\{\bE_2^{(1)}\} = \bzero\ .
\end{align*}
\end{remark}

It follows from this:
\begin{align*}
\tilde\bA &= (\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv \\
\bA_0 &=\bS^{(1)}{\bS^{(0)}}^\inv\ .
\end{align*}
Then:
\begin{align}
\nonumber
\bh^{(\ell)} &= \balpha^{(\ell)} - \balpha^{(\ell)}_0 \\
\nonumber
&= \be_M^T\left(\tilde\bA^\ell-\tilde\bA_0^\ell\right) \\
&= \be_M^T\left(\left((\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\right)^\ell- \tilde\bA_0^\ell\right)\ .
\label{eq:error.vec}
\end{align}

\subsection{Study of $\bh^{(\ell)}$}
The randomness of $\bh^{(\ell)}$ is completely originating from the error matrices. Besides, notice that the first $M-1$ rows in $\bE^{(1)}$ are the same as the last $M-1$ rows of $\bE^{(0)}$. Thus, we gather all the sources of randomness into an vector $\bg\in\RR^{M(M+1)}$ defined as:
\[
\bg = \vec\left(
\begin{pmatrix}
\bE^{(0)} \\
\be_M^T\bE^{(1)}
\end{pmatrix}
\right)\ .
\]
Here, "$\vec$" denotes the vectorization operator, concatenating the columns of a given matrix on top of one another. Then, by definition, we have:
\[
\bg = \sigma\bg_1 + \sigma^2\bg_2\ ,
\]
where:
\begin{align*}
\bg_1 &= \dfrac1K\sum_{k=0}^{K-1}\vec\left( \tilde\bz_k\bw_k^T + \tilde\bw_k\bz_k^T \right) \\
\bg_2 &= \dfrac1K\sum_{k=0}^{K-1}\vec\left(\tilde\bw_k\bw_k^T-\tilde\bI \right) \ .
\end{align*}
with $\tilde\bz_k^T= \begin{pmatrix} \bz_k^T & \bz_{k+1}[0] \end{pmatrix}$ and $\tilde\bw_k^T= \begin{pmatrix} \bw_k^T & \bw_{k+1}[0] \end{pmatrix}$. Then, $\bg_1$ is a Gaussian random vector as a linear combination of Gaussian random vectors. Moreover, using the central limit theorem under weak dependence, we can show that $\bg_2$ also converges towards a Gaussian random vector as $K\to\infty$. Combining these two results gives the following result:
\[
\sqrt{K}\ \bg \xrightarrow[K\to\infty]{\cD} \cN(\bzero,\bGamma_0)\ ,
\]
where $\bGamma_0=\EE\left\{\bg\bg^T\right\}$ is a covariance matrix.

Furthermore, one can write $\bh^{(\ell)}$ as $\bh^{(\ell)}=f^{(\ell)}(\bg)$ where $f^{(\ell)}$ is a deterministic function such that:
\begin{align*}
f^{(\ell)} : \RR^{M(M+1)} &\to \RR^{M} \\
 \bg &\mapsto \bh^{(\ell)}\ . \\
\end{align*}
Then, as $f^{(\ell)}$ is a differentiable function, using the Delta method gives:
\begin{align*}
\sqrt{K}\ \bh^{(\ell)} \xrightarrow[K\to\infty]{\cD} \cN(\bzero,{\bF^{(\ell)}}^T\bGamma_0\bF^{(\ell)})\ ,
\end{align*}
where $\bF^{(\ell)}$ is the Jacobian matrix such that:
\[
\bF^{(\ell)}[m,m'] = \left.\dfrac{\partial f^{(\ell)}_m}{\partial\bg[m']}\right\vert_{\bg=\bzero}\ .
\]

@@

\subsection{Expression of the bias $\bmu$.}

@@

@@

\EE\{\bh^{(\ell)}\} &\underset{K\to\infty}{\longrightarrow} 0\\
\EE\{\bh^{(\ell)}\bw_{K}\} &\underset{K\to\infty}{\longrightarrow} 0

@@

\label{eq:bias.ap}

@@

\subsection{Expression of the covariance $\bgamma$.}
We recall that $n>N$, we consequently denote $n=N-1+\ell$.  To derive the covariance, let us segregate the cases.

\paragraph{If $n'\in I^2$}
From Lemma~1, we have that $h^{(\ell)}$ is asymptotically Gaussian. Then, as a direct consequence of the Isserlis' theorem, odd-order moments are vanishing. Then, combining result~\eqref{eq:bias.ap} and equation~\eqref{eq:bias0}, we obtain:
\begin{align*}
\bgamma[n,n'] &= \sigma\EE\{\bw[n']\bh^{(\ell)}\}\bz_K + \sigma^2\balpha_0^{(\ell)}\EE\{\bw_K\bw[n']\} + o(\sigma^2) \ .
\end{align*}
We remark that
\[
\balpha_0^{(\ell)}\EE\{\bw_K\bw[n']\}=\balpha_0^{(\ell)}[n'-(N-M)]\1_{(n'\geq N-M)}\ .
\]
Moreover, using Delta method one can show that we have the asymptotic result:
\begin{equation}
\EE\{\bw[n']\bh^{(\ell)}\} \underset{K\to\infty}{\longrightarrow} 0
\label{eq:cov.ap}
\end{equation}
Finally:
\begin{align*}
\bgamma[n,n'] &\underset{K\to\infty}{\sim} \sigma^2\balpha_0^{(\ell)}[n'-(N-M)]\1_{(n'\geq N-M)} + o(\sigma^2) \ .
\end{align*}

\paragraph{If $n'\geq N$}
From Lemma~1, we have that $h^{(\ell)}$ is asymptotically Gaussian. Then, as a direct consequence of the Isserlis' theorem, odd-order moments are vanishing. Then, combining result~\eqref{eq:bias.ap} and equations~\eqref{eq:cov0} and~\eqref{eq:cov.ap}, we obtain:
\begin{align*}  
\bgamma[n,n'] &= \bz_K^T\EE\left\{{\balpha^{(\ell)}}^T\balpha^{(\lambda)}\right\}\bz_K + \sigma\EE\{\balpha^{(\ell)}\bw_K\balpha^{(\lambda)}\}\bz_K+ \sigma\EE\{\balpha^{(\lambda)}\bw_K\balpha^{(\ell)}\}\bz_K \\
& +\sigma^2\EE\{\balpha^{(\ell)}\bw_K\balpha^{(\lambda)}\bw_K\}-\bz[n]\bz[n']+o(\sigma^2) \\
&= \bz_K^T\EE\left\{{\bh^{(\ell)}}^T\bh^{(\lambda)}\right\}\bz_K + \balpha_0^{(\ell)}\sigma\EE\{\bw_K\bh^{(\lambda)}\}\bz_K + \sigma\EE\{\bh^{(\ell)}\bw_K\}\bz[n']  \\
&+ \sigma\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\}\bz_K+ \sigma\EE\{\bh^{(\lambda)}\bw_K\}\bz[n] + \sigma\balpha_0^{(\lambda)}\EE\{\bw_K\bh^{(\ell)}\}\bz_K \\
& + \sigma\EE\{\bh^{(\lambda)}\bw_K\bh^{(\ell)}\}\bz_K+\sigma^2\balpha_0^{(\ell)}\EE\{\bw_K\bh^{(\lambda)}\bw_K\}+\sigma^2\balpha_0^{(\lambda)}\EE\{\bw_K\bh^{(\ell)}\bw_K\} \\
&+\sigma^2\left\langle\balpha^{(\ell)},\balpha^{(\lambda)}\right\rangle +\sigma^2\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\bw_K\} + o(\sigma^2) \\
&\underset{K\to\infty}{\sim} \dfrac1K\bz_K^T\bGamma^{(\ell,\lambda)}\bz_K +\sigma^2\left\langle\balpha^{(\ell)},\balpha^{(\lambda)}\right\rangle +\sigma^2\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\bw_K\} + o(\sigma^2)
\end{align*}
The Isserlis' theorem also gives the following result:
\begin{align*}
\EE\{\bh^{(\ell)}\bw_K\bh^{(\lambda)}\bw_K\} &= \sum_{m,m'=0}^{M-1}\EE\{\bh^{(\ell)}[m]\bw_K[m]\bh^{(\lambda)}[m']\bw_K[m']\} \\
&= \sum_{m,m'=0}^{M-1}\EE\{\bh^{(\ell)}[m]\bw_K[m]\}\EE\{\bh^{(\lambda)}[m']\bw_K[m']\} + \EE\{\bh^{(\ell)}[m]\bw_K[m']\}\EE\{\bh^{(\lambda)}[m']\bw_K[m]\} \\
&\hspace{35pt} + \EE\{\bh^{(\ell)}[m]\bh^{(\lambda)}[m']\}\underbrace{\EE\{\bw_K[m]\bw_K[m']\}}_{=\delta_{m,m'}} \\
&\underset{K\to\infty}{\sim} \sum_{m=0}^{M-1} \EE\{\bh^{(\ell)}[m]\bh^{(\lambda)}[m]\} = \dfrac1K\Tr\left(\bGamma^{(\ell,\lambda)}\right)\ .
\end{align*}
We conclude that:
\begin{align*}  
\bgamma[n,n'] &\underset{K\to\infty}{\sim} \dfrac1K\bz_K^T\bGamma^{(\ell,\lambda)}\bz_K +\sigma^2\left\langle\balpha^{(\ell)},\balpha^{(\lambda)}\right\rangle +\dfrac{\sigma^2}{K}\Tr\left(\bGamma^{(\ell,\lambda)}\right) + o(\sigma^2)\ .
\end{align*}

%\begin{align*}
%\bgamma[\ell,\ell] &\leq \dfrac1K\left(\sqrt{\bz_K^T\EE\{{\bu^{(\ell)}}^T\bu^{(\ell)}\}\bz_K} + \sigma\sqrt{\EE\{(\bu^{(\ell)}\bw_K)^2\}}\right)^2 \\
%&\ + \dfrac{2\sigma}{\sqrt{K}}\|\balpha_0^{(\ell)}\|\left(\sqrt{\bz_K^T\EE\{{\bu^{(\ell)}}^T\bu^{(\ell)}\}\bz_K} +\sigma\sqrt{\EE\{(\bu^{(\ell)}\bw_K)^2\}} \right)+ \sigma^2\|\balpha_0^{(\ell)}\|^2 - \bmu[\ell]^2 + o(\sigma^2) \\
%\end{align*}
%
%Then, Isserlis formula gives us:
%\begin{align*}
%\EE\{(\bu^{(\ell)}\bw_K)^2\} &= \sum_{m,m'=0}^{M-1}\EE\{\bu^{(\ell)}[m]\bw_K[m]\bu^{(\ell)}[m']\bw_K[m']\}\\
%&\underset{K\to\infty}{\sim} \sum_{m,m'=0}^{M-1}\EE\{\bu^{(\ell)}[m]\bw_K[m]\}\EE\{\bu^{(\ell)}[m']\bw_K[m']\}+\EE\{\bu^{(\ell)}[m]\bu^{(\ell)}[m']\}\EE\{\bw_K[m]\bw_K[m']\} \\
%&\hspace{30pt}+\EE\{\bu^{(\ell)}[m]\bw_K[m']\}\EE\{\bu^{(\ell)}[m']\bw_K[m]\}\\
%&\leq \Tr(\bGamma^{(\ell)}) + 2\sum_{m,m'=0}^{M-1}\sqrt{\bGamma^{(\ell)}[m,m]\bGamma^{(\ell)}[m',m']}
%\end{align*}
%So:
%\begin{align*}
%\bgamma[\ell,\ell] &\leq \dfrac1K\left(\sqrt{\bz_K^T\bGamma^{(\ell)}\bz_K} + \sigma\sqrt{\Tr(\bGamma^{(\ell)}) + 2\sum_{m,m'=0}^{M-1}\sqrt{\bGamma^{(\ell)}[m,m]\bGamma^{(\ell)}[m',m']}}\right)^2 \\
%&\ + \dfrac{2\sigma}{\sqrt{K}}\|\balpha_0^{(\ell)}\|\left(\sqrt{\bz_K^T\bGamma^{(\ell)}\bz_K} +\sigma\sqrt{\Tr(\bGamma^{(\ell)}) + 2\sum_{m,m'=0}^{M-1}\sqrt{\bGamma^{(\ell)}[m,m]\bGamma^{(\ell)}[m',m']}} \right)+ \sigma^2\|\balpha_0^{(\ell)}\|^2 + o(\sigma^2) \\
%\end{align*}
